\title{Message from the Authors}
\vskip 0.2in

\noindent Dear Reviewers,

\vskip 0.1in

\noindent We thank you for your constructive comments, which have allowed us 
to improve the quality of the manuscript. We have addressed the comments and 
incorporated your valuable suggestions in the revised manuscript, in particular 
highlighting the key contributions and significance of this work.\\ 

\noindent We have made the following major changes to the original manuscript:

\begin{enumerate}
  \item \textbf{Change in title:}
    We have changed the title by removing the adjective
    novel and adding terms to better represent the contributions in the paper.
  \item \textbf{Addition of contributions in Abstract}:
    We have added four major
    contributions in the abstract. We have also added the evaluation result
    scores to quantify the significance of the proposed method well ahead.
  \item \textbf{Improvement in the Introductions section:}
    The introduction section has been modified to get into the specific
    challenges involved in pre-processing of Devanagari scripts quickly,
    removing the unnecessary background. Likewise, several references of works 
    done in stemming of Devanagari scripts have been added. 
  \item \textbf{Addition of Discussions and Comparisons sub-section:}
    A separate sub-section has been added under the section "VI. Results and
    Discussions" to discuss about the limitations in existing stemming
    approaches in Devanagari scripts, the changes adopted in the proposed method
    from previous rule-based methods, and significance of the approach in detail with
    comparisons of scores with other methods.
  \item \textbf{Introduction of new publicly available dataset:}
    A new publicly available dataset called NEP-PLAG2019v1 has been introduced,
    which is supposed to contain 10,000 pairs of annotated Nepali news articles
    with plagiarism class labels. However, this dataset is not available yet and
    is a work for future. 
  \item \textbf{Addition of Experiments:}
    The original experiments have been conducted on the newly introduced
    dataset, consisting of 10,000 pairs of articles
    instead of small 100 pairs of articles. Further experiments have been added
    to compare the results of the proposed method with previous similar
    approaches.
  \item \textbf{Improvement in visibility of figures:}
    Figures have been made more clear and large figure has been rendered in a
    complete separate page for better visibility.
\end{enumerate}

\noindent We address each comment separately in the following detailed response. 
The comments we received are boxed, and our responses are written following each 
comment. All page and reference numbers in our response are based on the revised 
manuscript, unless otherwise stated. The page and reference numbers mentioned in 
the reviewers' comments are kept intact and are based on the original manuscript. 
We look forward to 
hearing from you and hope that you find the revised manuscript satisfactory.
\vskip 0.2in

\noindent Sincerely, \\
\noindent Ayush Kumar Shah

