\section{Response to Reviewer \#2 (Murtaza Tamjeed)}
% \subsection*{Overall Comments}
% \begin{mdframed}
% \begin{quote}
% 	 Reviewer \# 2 - Overall Comments here
% \end{quote}
% \end{mdframed}

% \subsection{Response} 
% We would like to thank you for you positive feedback. Your detailed comments have considerably helped with improving the clarity of the revised manuscript.

% \noindent\rule{17cm}{2.0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reviewer Comment}
\begin{mdframed}
\begin{quote}
	Preprocessing a
foreign language text is a great contribution; however, for plagiarism detection,
there are many more factors to consider. Presence of the common base forms of
the words in two articles may not guarantee plagiarism. Some other factors that
need to be considered for plagiarism detection might include, context, sentence
level similarity, and document level similarity.
\end{quote}
\end{mdframed}

\subsection{Response} 
We agree that there are several factors to consider for plagiarism detection
like the ones mentioned by the reviewer. We have included them as part of the
limitations and future work in the VII. Conclusion section. The current approach
has produced fair results for the dataset being used, hence we have retained the
main approach in the paper.\\


\noindent\rule{17cm}{2.0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reviewer Comment}
\begin{mdframed}
\begin{quote}
Also, the statistical measures reported are from 20 pairs of manually
annotatedarticles. These measures might not hold true on real plagiarized
texts. This workwould have been improved if the author had trained and tested
the algorithmson larger set of real plagiarized and non-plagiarized text.
\end{quote}
\end{mdframed}

\subsection{Response} 
We have introduced a new dataset called NEP-PLAG2019v1, consisting of 10,000
pairs of articles and experiments have been added on the new dataset. 
Please refer to the 'Introduction to new publicly available dataset'
and 'Addition of Experiments' points in the major changes summary.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent\rule{17cm}{6.0pt}
